---
title: "Untitled"
format: html
editor: visual
---

```{r}
pacman::p_load(here, doSPSS, tidyverse, psych, ez, effectsize, patchwork)
Theme <- theme(axis.text.x = element_text(size = 20),
        axis.text.y = element_text(size = 20),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text = element_text(size = 20),
        legend.title = element_text(size = 20),
        title = element_text(size = 20)) 
Data_6_light <- readRDS(here("Data//Data_6_light.rds")) 
# Data_6_severe <- readRDS(here("Data//Data_6_severe.rds")) 

```

# Age and gender

## Goodness of fit

```{r}

table(Data_6$Gender)
(100 * table(Data_6$Gender) / nrow(Data_6)) %>%
  round(1)

skim(Data_6$Age.x)

```

```{r}
Data_6_light %>% 
  select(Competent, Intelligent, Educated, Professional, Experienced, Qualified
                                                , Sincere, Honest, Just, Fair
                                                , Moral, Ethical, Responsible, Considerate) %>% 
  alpha()
Data_6_severe %>% 
  select(Competent, Intelligent, Educated, Professional, Experienced, Qualified
                                                , Sincere, Honest, Just, Fair
                                                , Moral, Ethical, Responsible, Considerate) %>% 
  alpha()

Data_6_light %>% 
  select(Competent, Intelligent, Educated, Professional, Experienced, Qualified) %>% 
  alpha()

Data_6_light %>% 
  select(
                                                 Sincere, Honest, Just, Fair
                                                ) %>% 
  alpha()

Data_6_light %>% 
  select( Moral, Ethical, Responsible, Considerate) %>% 
  alpha()
```

# METI overall


## Three way model

No three way interaction.
```{r, warning=FALSE, message=FALSE}
ez::ezANOVA(data      = Data_6_light
            , dv      = METI_overall
            , wid     = Q1
            , between = c(know_IDK, doc_lay, just_noJust)
            , type    = 3
            , return_aov = TRUE
            , detailed   = FALSE

            , white.adjust = FALSE)


Data_6_light %>%
    group_by(know_IDK, doc_lay, just_noJust) %>%
  summarise(round(mean_cl_normal(METI_overall), 2)
            , N = length(METI_overall))


data_6_fig_meti_three_way <- Data_6_light %>% 
  mutate(`Reply type` = know_IDK
         , doc_lay = if_else(doc_lay == 'doc', 'Physician', 'Layperson')
         , just_noJust = if_else(just_noJust == 'just', 'Justified', 'Non justified')) %>% 
  ggplot(aes(x = doc_lay, y = METI_overall, fill = `Reply type`)) +
  # geom_violin(alpha = 0) +
   stat_summary(fun.data = "mean_cl_normal", geom = "errorbar", color = "black", width = 0.4, linewidth = 2, position = position_dodge(0.9)) +
    stat_summary(fun = mean, geom = "bar", alpha = 0.8, position = position_dodge(0.9)) +
  scale_fill_manual(values = c("grey30", "grey80")) +
  scale_y_continuous(breaks = seq(from = 1, to = 10, by = 1)) +
       geom_point(aes(color = `Reply type`), position = position_jitterdodge(jitter.width = 0.2, jitter.height = 0), size = 1) + 
  scale_fill_manual(values =  c("grey30", "grey80")) +
  xlab('') + ylab('') +
  ggtitle('METI') +
  theme_bw() +
        scale_color_manual(values = c("grey0", "grey0")) +  # Set the point colors to gray
  Theme +
  facet_wrap(~ just_noJust) +
  theme(
   strip.text.x = element_text(
      size=20
     )
   ) +          theme(legend.position = "none")

 





Data_6_light <- 
Data_6_light %>% 
  mutate(con = paste0(doc_lay, '_', know_IDK, '_', just_noJust))

postHoc(Data_6_light$METI_overall, Data_6_light$con, Correction  = 'bonfferroni')
```

## know_IDK Main effect: IDK > know
```{r, warning=FALSE, message=FALSE}
Data_6_light %>% 
  group_by(know_IDK) %>% 
  summarise(round(mean_cl_normal(METI_overall), 2)
            , N = length(METI_overall))
```

## doc_lay Main effect: doc > lay
```{r, warning=FALSE, message=FALSE}
Data_6_light %>% 
  group_by(doc_lay) %>% 
  summarise(round(mean_cl_normal(METI_overall), 2)
            , N = length(METI_overall))
```

## know_IDK * just_noJust: just IDK > just know (p = .050)
```{r, warning=FALSE, message=FALSE}
Data_6_light %>% 
  group_by(know_IDK, just_noJust) %>% 
  summarise(round(mean_cl_normal(METI_overall), 2)
            , N = length(METI_overall))
meti_2 <- 

Data_6_light %>% 
  ggplot(aes(x = just_noJust, y = METI_overall, fill = know_IDK)) +
  # geom_violin(alpha = 0) +
   stat_summary(fun.data = "mean_cl_normal", geom = "errorbar", color = "black", width = 0.2, linewidth = 1, position = position_dodge(0.9)) +
    stat_summary(fun = mean, geom = "bar", alpha = 0.2, position = position_dodge(0.9)) +
  scale_fill_manual(values = c("grey30", "grey80")) +
  scale_y_continuous(breaks = seq(from = 1, to = 10, by = 1)) +
  xlab('Justification') + ylab('METI') +
  guides(fill = guide_legend(title = "Answer")) +
  ggtitle('METI') +
  theme_bw() +
  Theme

fit1 <- lm(METI_overall ~ just_noJust * know_IDK , data = Data_6_light)
emmeans::emmeans(fit1, specs = pairwise ~  just_noJust * know_IDK, adjust = 'bonf')
```

# Expertise
## Three way model

No three way interaction.

```{r, warning=FALSE, message=FALSE}
Data_6_light %>%
    group_by(know_IDK, doc_lay, just_noJust) %>%
  summarise(round(mean_cl_normal(Expertise), 2)
            , N = length(Expertise))

ez::ezANOVA(data      = Data_6_light
            , dv      = Expertise
            , wid     = Q1
            , between = c(know_IDK, doc_lay, just_noJust)
            , type    = 3
            , return_aov = TRUE
            , detailed   = FALSE

            , white.adjust = FALSE)

ez::ezANOVA(data      = Data_6_light
            , dv      = Expertise
            , wid     = Q1
            , between = c(know_IDK, doc_lay, just_noJust)
            , type    = 3
            , return_aov = TRUE
            , detailed   = FALSE
            , white.adjust = TRUE)


data_6_fig_expertise_three_way <- Data_6_light %>% 
  mutate(`Reply type` = know_IDK
         , doc_lay = if_else(doc_lay == 'doc', 'Physician', 'Layperson')
         , just_noJust = if_else(just_noJust == 'just', 'Justified', 'Non justified')) %>% 
  ggplot(aes(x = doc_lay, y = Expertise, fill = `Reply type`)) +
  # geom_violin(alpha = 0) +
   stat_summary(fun.data = "mean_cl_normal", geom = "errorbar", color = "black", width = 0.4, linewidth = 2, position = position_dodge(0.9)) +
    stat_summary(fun = mean, geom = "bar", alpha = 0.8, position = position_dodge(0.9)) +
  scale_fill_manual(values = c("grey30", "grey80")) +
  scale_y_continuous(breaks = seq(from = 1, to = 10, by = 1)) +
       geom_point(aes(color = `Reply type`), position = position_jitterdodge(jitter.width = 0.2, jitter.height = 0), size = 1) + 
  scale_fill_manual(values =  c("grey30", "grey80")) +
  xlab('') + ylab('') +
  ggtitle('Expertise') +
  theme_bw() +
        scale_color_manual(values = c("grey0", "grey0")) +  # Set the point colors to gray
  Theme +
  facet_wrap(~ just_noJust) +
  theme(
   strip.text.x = element_text(
      size=20
     )
   ) 


data_6_fig_meti_three_way
data_6_fig_expertise_three_way
data_6_fig_integrity_three_way
```

## just_noJust main effect: Just > no just
```{r, warning=FALSE, message=FALSE}
Data_6_light %>%
    group_by(just_noJust) %>%
  summarise(round(mean_cl_normal(Expertise), 2)
            , N = length(Expertise))
```

## doc_lay main effect: doc > lay

```{r, warning=FALSE, message=FALSE}
Data_6_light %>%
    group_by(doc_lay) %>%
  summarise(round(mean_cl_normal(Expertise), 2)
            , N = length(Expertise))
```

## just_noJust * know_IDK: know no just > IDK no just
```{r, warning=FALSE, message=FALSE}
Data_6_light %>%
    group_by(just_noJust, know_IDK) %>%
  summarise(round(mean_cl_normal(Expertise), 2)
            , N = length(Expertise))

exp_2 <- 
Data_6_light %>% 
  ggplot(aes(x = just_noJust, y = Expertise, fill = know_IDK)) +
  # geom_violin(alpha = 0) +
   stat_summary(fun.data = "mean_cl_normal", geom = "errorbar", color = "black", width = 0.2, linewidth = 1, position = position_dodge(0.9)) +
    stat_summary(fun = mean, geom = "bar", alpha = 0.2, position = position_dodge(0.9)) +
  scale_fill_manual(values = c("grey30", "grey80")) +
  scale_y_continuous(breaks = seq(from = 1, to = 10, by = 1)) +
  xlab('Justification') + ylab('METI') +
  guides(fill = guide_legend(title = "Answer")) +
  ggtitle('Expertise') +
  theme_bw() +
  Theme
  
fit2 <- lm(Expertise ~ just_noJust * know_IDK, data = Data_6_light)
emmeans::emmeans(fit2, specs = pairwise ~ just_noJust * know_IDK, adjust = 'bonf')

(meti_2 + exp_2)
```

# METI Integrity

```{r, warning=FALSE, message=FALSE}
Data_6_light %>%
    group_by(know_IDK, doc_lay, just_noJust) %>%
  summarise(round(mean_cl_normal(Integrity), 2)
            , N = length(Integrity))

ez::ezANOVA(data      = Data_6_light
            , dv      = Integrity
            , wid     = Q1
            , between = c(know_IDK, doc_lay, just_noJust)
            , type    = 3
            , return_aov = TRUE
            , detailed   = FALSE

            , white.adjust = FALSE)

data_6_fig_integrity_three_way <- 
Data_6_light %>% 
  mutate(`Reply type` = know_IDK
         , doc_lay = if_else(doc_lay == 'doc', 'Physician', 'Layperson')
         , just_noJust = if_else(just_noJust == 'just', 'Justified', 'Non justified')) %>% 
  ggplot(aes(x = doc_lay, y = Integrity, fill = `Reply type`)) +
  # geom_violin(alpha = 0) +
   stat_summary(fun.data = "mean_cl_normal", geom = "errorbar", color = "black", width = 0.4, linewidth = 2, position = position_dodge(0.9)) +
    stat_summary(fun = mean, geom = "bar", alpha = 0.8, position = position_dodge(0.9)) +
  scale_fill_manual(values = c("grey30", "grey80")) +
  scale_y_continuous(breaks = seq(from = 1, to = 10, by = 1)) +
       geom_point(aes(color = `Reply type`), position = position_jitterdodge(jitter.width = 0.2, jitter.height = 0), size = 1) + 
  scale_fill_manual(values =  c("grey30", "grey80")) +
  xlab('') + ylab('') +
  ggtitle('Integrity') +
  theme_bw() +
        scale_color_manual(values = c("grey0", "grey0")) +  # Set the point colors to gray
  Theme +
  facet_wrap(~ just_noJust) +
  theme(
   strip.text.x = element_text(
      size=20
     )
   ) +
  theme(legend.position = "none")


```

know_IDK main effect: IDK > know
```{r, warning=FALSE, message=FALSE}
Data_6_light %>%
    group_by(know_IDK) %>%
  summarise(round(mean_cl_normal(Integrity), 2)
            , N = length(Integrity))

```

doc_lay main effect: doc > lay
```{r, warning=FALSE, message=FALSE}
Data_6_light %>%
    group_by(doc_lay) %>%
  summarise(round(mean_cl_normal(Integrity), 2)
            , N = length(Integrity))
```



# METI Benevolence

```{r, warning=FALSE, message=FALSE}
Data_6_light %>%
    group_by(know_IDK, doc_lay, just_noJust) %>%
  summarise(round(mean_cl_normal(Benevolence), 2)
            , N = length(Benevolence))

  ez::ezANOVA(data      = Data_6_light
            , dv      = Benevolence
            , wid     = Q1
            , between = c(know_IDK, doc_lay, just_noJust)
            , type    = 3
            , return_aov = TRUE
            , detailed   = FALSE
            , white.adjust = FALSE)

data_6_fig_benevolence_three_way <-     
Data_6_light %>% 
  mutate(`Reply type` = know_IDK
         , doc_lay = if_else(doc_lay == 'doc', 'Physician', 'Layperson')
         , just_noJust = if_else(just_noJust == 'just', 'Justified', 'Non justified')) %>% 
  ggplot(aes(x = doc_lay, y = Benevolence, fill = `Reply type`)) +
  # geom_violin(alpha = 0) +
   stat_summary(fun.data = "mean_cl_normal", geom = "errorbar", color = "black", width = 0.4, linewidth = 2, position = position_dodge(0.9)) +
    stat_summary(fun = mean, geom = "bar", alpha = 0.8, position = position_dodge(0.9)) +
  scale_fill_manual(values = c("grey30", "grey80")) +
  scale_y_continuous(breaks = seq(from = 1, to = 10, by = 1)) +
       geom_point(aes(color = `Reply type`), position = position_jitterdodge(jitter.width = 0.2, jitter.height = 0), size = 1) + 
  scale_fill_manual(values =  c("grey30", "grey80")) +
  xlab('') + ylab('') +
  ggtitle('Benevolence') +
  theme_bw() +
        scale_color_manual(values = c("grey0", "grey0")) +  # Set the point colors to gray
  Theme +
  facet_wrap(~ just_noJust) +
  theme(
   strip.text.x = element_text(
      size=20
     )
   ) +
  theme(legend.position = "none")

(data_6_fig_meti_three_way +
data_6_fig_expertise_three_way +
data_6_fig_integrity_three_way +
data_6_fig_benevolence_three_way)


```

know_IDK main effect: IDK > know
```{r, warning=FALSE, message=FALSE}
Data_6_light %>%
    group_by(know_IDK) %>%
  summarise(round(mean_cl_normal(Benevolence), 2)
            , N = length(Benevolence))
```

doc_lay main effect: doc > lay
```{r, warning=FALSE, message=FALSE}
Data_6_light %>%
    group_by(doc_lay) %>%
  summarise(round(mean_cl_normal(Benevolence), 2)
            , N = length(Benevolence))
```

# Complaience

```{r, warning=FALSE, message=FALSE}
ez::ezANOVA(data      = Data_6_light
            , dv      = Complaience
            , wid     = Q1
            , between = c(know_IDK, doc_lay, just_noJust)
            , type    = 3
            , return_aov = TRUE
            , detailed   = FALSE

            , white.adjust = FALSE)
ez::ezANOVA(data      = Data_6_light
            , dv      = Complaience
            , wid     = Q1
            , between = c(know_IDK, doc_lay, just_noJust)
            , type    = 3
            , return_aov = TRUE
            , detailed   = FALSE

            , white.adjust = TRUE)


Data_6_light %>% 
  group_by(know_IDK, doc_lay, just_noJust) %>% 
  summarise(round(mean_cl_normal(Complaience), 2)
            , N = length(Complaience))


data_6_fig_compliance_three_way <- 
Data_6_light %>% 
  ggplot(aes(x = just_noJust , y = Complaience, fill = know_IDK)) +
   ggplot2::stat_summary(fun.data = "mean_cl_normal", geom = "errorbar", color = "black", width = 0.2, linewidth = 1, position = position_dodge(0.9)) +
    ggplot2::stat_summary(fun = mean, geom = "bar", alpha = 0.2, position = position_dodge(0.9)) +
    ggplot2::theme_bw() +
    scale_fill_manual(values = c("grey30", "grey80")) +
  scale_y_continuous(breaks = seq(from = 1, to = 10, by = 1)) +
  Theme +
  ggtitle('Compliance') +
  facet_wrap(~doc_lay)
```

know_IDK main effect: IDK > know
```{r, warning=FALSE, message=FALSE}
Data_6_light %>% 
  group_by(know_IDK) %>% 
  summarise(round(mean_cl_normal(Complaience), 2)
            , N = length(Complaience))
```

doc_lay main effect: doc > lay
```{r, warning=FALSE, message=FALSE}
Data_6_light %>% 
  group_by(doc_lay) %>% 
  summarise(round(mean_cl_normal(Complaience), 2)
            , N = length(Complaience))
```

doc_lay * know_IDK: the delta for layperson is greater
Interesting that the compliance for layperson IDK is greater than physician know
```{r, warning=FALSE, message=FALSE}
Data_6_light %>% 
  group_by(know_IDK, doc_lay) %>% 
  summarise(round(mean_cl_normal(Complaience), 2)
            , N = length(Complaience))

Data_6_light %>% 
  ggplot(aes(x = doc_lay, y = Complaience, fill = know_IDK)) +
   ggplot2::stat_summary(fun.data = "mean_cl_normal", geom = "errorbar", color = "red", width = 0.2, linewidth = 1, position = position_dodge(0.9)) +
    ggplot2::stat_summary(fun = mean, geom = "bar", alpha = 0.2, position = position_dodge(0.9)) +
    ggplot2::theme_bw() +
  scale_y_continuous(breaks = seq(from = 1, to = 10, by = 1)) +
  Theme


fit3 <- lm(Complaience ~ doc_lay * know_IDK, data = Data_6_light)
emmeans::emmeans(fit3, specs = pairwise ~ doc_lay * know_IDK, adjust = 'bonf')
```

## Three way interaction logistic regression

```{r}
Data_6_light %>% select(full_condition, bin_faces) %>% table()
Data_6_light %>% select(full_condition, odd_is_male) %>% table()

face_Data_6 <- Data_6_light %>%
  drop_na(male_participant)

CT(Data_6_light$bin_faces, Data_6_light$vlaKnowledge_bin)
indttest(Data_6_light$Age.x, Data_6_light$bin_faces)

regLog1 <- stats::glm(male_face ~ just_noJust * know_IDK * doc_lay + male_participant #* male_participant
                        , family = binomial('logit'), data = face_Data_6)   # Performing a logistic regression

ORCI    <- round(exp(cbind(Odds_Ratios = stats::coef(regLog1), stats::confint(regLog1))), 2)  # Calculation odds ratios and confidance intervales for the odds ratios

  cdiff           <- round(regLog1$null.deviance - regLog1$deviance, 2)  # Calculating the Chi square value of the model
  dfdiff          <- regLog1$df.null - regLog1$df.residual              # Calculating the degrees of freedom value of the model
  p               <- round(stats::pchisq(q = cdiff, df = dfdiff, lower.tail = FALSE), 100) # Calculating the p value of the model
  Nagelkerke      <- rcompanion::nagelkerke(fit = regLog1, null = NULL, restrictNobs = FALSE)  # Calculating the explained variance
  NagelkerkePrint <- paste0(100 * round(Nagelkerke$Pseudo.R.squared.for.model.vs.null[3], 4), "%") # Extracting the explained variance

  Hoslem          <- ResourceSelection::hoslem.test(x = regLog1$y, y = fitted(regLog1), g = 10)  # Calculating the significance of the accuracy
  hoslemStatistic <- round(Hoslem$statistic, 2)
  hoslemP         <- round(Hoslem$p.value, 2)

  
  
face_Data_6 %>% 
  group_by(just_noJust, know_IDK, doc_lay) %>% 
  reframe(s = sum(male_face)
          , L = length(male_face)
            , ratio = 100 * s / L) %>%
  distinct() %>% 
ggplot(aes(x = just_noJust, y = ratio, fill = know_IDK, color = know_IDK)) + 
  geom_bar(stat = "identity", position = "dodge")  +
  theme_bw() +
  facet_grid(~doc_lay)  
  
    
face_Data_6 %>% 
  filter(male_participant == 1) %>% 
  group_by(just_noJust, know_IDK, doc_lay) %>% 
  reframe(s = sum(male_face)
          , L = length(male_face)
            , ratio = 100 * s / L) %>%
    distinct() %>% 
ggplot(aes(x = just_noJust, y = ratio, fill = know_IDK, color = know_IDK)) + 
  geom_bar(stat = "identity", position = "dodge")  +
  theme_bw() +
  facet_grid(~doc_lay)

face_Data_6 %>% 
  filter(male_participant != 1) %>% 
  group_by(just_noJust, know_IDK, doc_lay) %>% 
  reframe(s = sum(male_face)
          , L = length(male_face)
            , ratio = 100 * s / L) %>%
    distinct() %>% 
ggplot(aes(x = just_noJust, y = ratio, fill = know_IDK, color = know_IDK)) + 
  geom_bar(stat = "identity", position = "dodge")  +
  theme_bw() +
  facet_grid(~doc_lay)




face_Data_6 %>% 
  group_by(just_noJust, know_IDK, doc_lay, male_participant) %>% 
  reframe(s = sum(male_face)
          , L = length(male_face)
            , ratio = 100 * s / L) %>%
    distinct() %>%  
    mutate(male_participant = if_else(male_participant == 1, 'Man', 'Woman')) %>% 
ggplot(aes(x = doc_lay, y = ratio, fill = know_IDK, color = know_IDK)) + 
  geom_bar(stat = "identity", position = "dodge")  +
  theme_bw() +
  facet_grid(~male_participant)



Data_6 %>% 
  select (bin_faces, doc_lay, know_IDK) %>% 
  table()




Data_6 %>% 
  select(know_IDK, bin_faces, male_participant) %>% 
  table()

Data_6 %>% 
  select(doc_lay, bin_faces, male_participant) %>% 
  table()

Data_6 %>% 
  select(just_noJust, bin_faces, male_participant) %>% 
  table()

CT(face_Data_6$bin_faces, face_Data_6$male_participant)
regLog1 <- stats::glm(male_face ~ male_participant 
                        , family = binomial('logit'), Data_6 = face_Data_6)   #
regLog1 %>% summary()

```
